\chapter{Introduction}

LogBlock is an online social media Service platform with a programming media sharing centrical view. The platform provides an easier and user-friendly means 
for both new and senior developers to share their open contributions without compromising too much on reachability of contents.

    \section{Purpose}
    The LogBlock Software Requirements Proposal is addressed to general team development members and business officers. 
    The specification provides high-level abstracted views on the Service's functional operations as well as initial descriptions on the system's constraints.
    The specification provides a developement contract applied to all personel of the developement team.

    \section{Intended Use}
    The proposal and occasional feature references in this document should be viewed as
    the descriptions of the software Services the system is expected to provide to  users and the constraints
    under which it must operate.
    \\\\
    Although some technical details may be included, this document \textbf{does not} enforces the inclusion of the defined implementation guides and should only act as a guidance
    to the desired outcomes of the system.
    %\\\\
    %The document should provide a comprehensive development contract requirements for synchronization and regularization on team performance. The contract acts as an 
    %ensurance for quality works and references for intended development cycles as well as appropriate actions of situations.
    \\\\
    Albeit usually up-to-date, consumers of this document should note that due to the ever-changing requirements as 
    well as the production model of the development organization, minors changes are to be introduced to accomodate with the needed alternation associated in each 
    development cycle's retrospective. And thus, it is advise to \textbf{revise} the document in known interval

    \section{Development Team Information}
    \begin{itemize}
        \item Team Leader, Project Manager: Hung K. Ngu (22127134) (nkhung22@clc.fitus.edu.vn)
        \item Executive Officer: Long T. Tran (22127249) (ttlong221@clc.fitus.edu.vn)
        \item Back-End Implementation Personel: An C. Trinh (22127004) (tcan22@clc.fitus.edu.vn)
        \item Front-End Implementation Personel: Cuong Ng. N. Tran (22127048) (tnncuong22@clc.fitus.edu.vn)
        \item Quality Assurance Personel: Long T. T. Nguyen (22127247) (nttlong22@clc.fitus.edu.vn) 
    \end{itemize}
    
\newpage

\chapter{Overall Description}
    \section{Service overview}
    The LogBlock Social Media Service (hence forward will be referenced as the Service) is a multi-media platform for \textbf{programming-based} content distributions, with a focus on 
    appealing interfaces and ease of access to code block \textbf{authoring tools} for interactive guides, code snippets. The Service aims to provide a personal profile space for content storage, while
    also encouraging \textbf{visibility} of knowledge via tailored exploration functionalities based on posts interaction. On a post-level, we provides a community-building scheme, allowing users
    to comment and react, share the content they are seeing, while also allowing \textbf{Experts} to recommend alternative solutions to the original posts.

    \section{User Classes and Characteristics}
    The Service is open to public usage, and partition users based on functional requirements as well as contributions to the platform.
    The intended user classes include four main classes: \textit{Guests, Registered user, Experts and Administrators}.
    \\\\
    \textbf{Guest} class provides a mean for public, new-come users to access shared content on the platform without explicitly register an operational account. Albeit the class
    is contrained to various functions of the Service, including: the ability to \textit{post}, the ability to generate interactions with posts via commenting and reaction and limited view of other registred user profiles.
    \\\\
    \textbf{Registered} class is considered to be the main targeted consumer of the platform. Registered users are generated through the platform's \textit{authentication system} and should be consistent
    until the  of such Service. Registered user can access almost all services provided by the platform as they are the targeted audience, and in turn, the platform is designed
    to best accomodate the changing needs and scalability of this user base.
    \\\\
    \textbf{Expert} class inherents all functionalities of the Registered class and provides a way for the platform administration to demonstrate \textit{verifiable} and \textit{trusted content}, as well as providing functionalities
    for expert individuals to reach their targeted audience in a controllable manners by means of higher post visibility and \textbf{Expert Suggested Solution}
    \\\\
    \textbf{Administrator} class is the gateway for the social developement team and moderators associated with the users' business organization to access the platform and uses tools that provide administration capabilities
    in order to enforce the Terms of Service of public usage. The administrator class also provides a mean for public users to flag and directly send reports to the moderating sections, allowing the ability to 
    quickly identify and resolve issues of other users.

    \section{Operating Environment}
    The platform primary operating is \textbf{Web Browsers}, offering extensibilities and incorperating OS features for ease of usage of the platform.
    The choice of platforms reflects the needs reach the maximum number of users while offering backwards compatibilities with user on older software or hardwares.

    \section{Constraints}
    The platform should respect Privacy and Data Protection. All user data must be securely stored, adhering to relevant privacy regulations (GDPR, CCPA).
    \\\\
    The platform should not promote hazardous contents and should not provide intervention methods to steer naratives or spread conspiracy.
    \\\\
    The system should handle large volumes of users and content uploads with minimized performance degradation. The system should provides a mean for administrator to monitor uptime and be notified
    of downtime as soon as possible.
    \\\\
    Based on the choice of Operating Environment, the design of User Interaction, User Experience should be consistent across different devices and browsers, offering Cross-Platform Compatibility.

    \section{Abstract Functional Requirements}
        \subsection{User Profile Management}
        \textbf{FR-0}: Users can be promoted from Guest to Registered by creating an account through the service dedicated authentication system.
        \\
        \textbf{FR-1}: Each Registered user is associated with a unique Handle. Each Registered user is in possession of a personal profile.
        \\
        \textbf{FR-2}: Registered Users can create, update, and delete their profiles.
        \\
        \textbf{FR-3}: Profile features include a profile picture, biography section (with character limit), and posts display.
        \\
        \textbf{FR-4}: Follower and following counts should be displayed on the profile page.
        \\
        \textbf{FR-5}: Registered Users can pin posts to their profiles.
        \\
        \textbf{FR-6}: Registered Users can privately view their activity log.

        \subsection{Abstract User Cross Interactions}
        \textbf{FR-7}: Provides a Follow/Unfollowing button for external Registered users to subscribe to the targeted profile.
        \\
        \textbf{FR-8}: Provides a Message button for external Registered users to directly message the recipient profile privately.
        \\
        \textbf{FR-9}: Provides a Block/Report button for external Registered users to report, isolate unwanted or harmful contents and notify the moderation team.
        
        \subsection{Content Sharing Block (Post)}
        \textbf{FR-10}: The content block should be visually appealing, but not obstructive and should corresponds to the flexible design of the platform.
        \\
        \textbf{FR-11}: The content block should be able to display original user's description, code block, as well as salient attachment through Markdown rendering.
        \\
        \textbf{FR-12}: Registered Users can upload images from device storage or drag-and-drop using the running OS functionality.
        \\
        \textbf{FR-13}: Registered Users can tag other users as co-contributor.
        \\
        \textbf{FR-14}: The captioning description should be limited to at most 1000 characters.
        \\
        \textbf{FR-15}: External Registered users can like, share and save content blocks.
        \\
        \textbf{FR-16}: External Registered users can comment on the content blocks, creating a sub-thread within the content block
        \\
        \textbf{FR-17}: Sub-thread comments can be liked, commented on, creating another sub-thread depth if it does not already exists.
        \\
        \textbf{FR-18}: Sub-thread comments depth should not exceed 3.

        \subsection{Content Feed, Exploration and Interaction}
        \textbf{FR-19}: External Registered Users content can be promoted to connected Registered users through the use of News Feed.
        \\
        \textbf{FR-20}: Registered Users can explore trending posts outside of own's connection through the Explorations page.
        \\
        \textbf{FR-21}: Exploration posts is sorted based on real time interaction rate, tags.
        \\
        \textbf{FR-22}: Registered Users can explore or connect with known associates through the search function, 
        the search function should find corresponding results based on display information and User Handle.
        \\
        \textbf{FR-23}: Search results should be locally stored.

        \subsection{Direct Messaging}
        \textbf{FR-24}: Registered Users can send and receive direct messages privately from external Registered users.
        \\
        \textbf{FR-25}: Direct messages are limited to markdown-compatible messages.
        \\
        \textbf{FR-26}: Direct message is limited to 500 characters per message.

        \subsection{Expert Requirements}
        \textbf{FR-27}: 
        \textbf{FR-27}:

        \subsection{Administrator Requirements}
        \textbf{FR-28}: User should not have the ability to access or leverage the functionalities of Administrator class without
        direct promotion from the moderation team.
        \\
        \textbf{FR-29}: Administrators must have the ability to monitor, flag, and remove content.
        \\
        \textbf{FR-30}: Administrators can issue warnings, suspend or ban accounts, and respond to flagged content.
        \\
        \textbf{FR-31}: Administrators can view Service-specific users and manage ad content.
        \\
        \textbf{FR-32}: Administrators can create help forum responses for users.

        \subsection{Real Time Interaction}
        \textbf{FR-33}: Real Time Interaction should provides up-to-date user-subscribed content status
        through real time means.
        \\
        \textbf{FR-34}: Real Time Interaction should be implemented through email nofitications in implementation.
        \\
        \textbf{FR-35}: Real Time Interaction should be rate-limited to 3 updates per minute.

        \subsection{Maintainability}
        \textbf{FR-36}: The system should be modular and maintainable, allowing for future expansions of features, including additional editing tools or messaging capabilities.
        \\
        \textbf{FR-37}: The codebase should follow industry best practices and be well-documented to enable easy updates and bug fixes.
\newpage

\chapter{Development Team Contract}

    \section{Development Team Roles and Responsibilities}
    Each team member should be responsible for the development of functionality descriptions as well as detailed
    implementation of the whole system due to the small team size.
    In order to provide a more reliable method of man­age­ment, the team role is defined as follow:
    \begin{itemize}
        \item Team Leader, Project Manager: Hung K. Ngu (22127134) (nkhung22@clc.fitus.edu.vn)
        \item Executive Officer: Long T. Tran (22127249) (ttlong221@clc.fitus.edu.vn)
        \item Implementation Personel: An C. Trinh (22127004) (tcan22@clc.fitus.edu.vn)
        \item Implementation Personel: Cuong Ng. N. Tran (22127048) (tnncuong22@clc.fitus.edu.vn)
        \item Implementation Personel: Long T. T. Nguyen (22127247) (nttlong22@clc.fitus.edu.vn) 
    \end{itemize}
    
    Project Manager should be responsible for the team coordination, performance and development documentation. 
    Project Manager is expected to apply development schemes and follows standard developement procedures in order to accurately
    track and maintain production quality.
    Project Manager should be responsible for reporting and finalizing production results to User.
    \\\\
    Executive Officer should be responsible for team specific production. Detailed development models is implemented based on Executive Office
    plan. Executice Officer is expected to finalize each modular functionalities of the product system specification.
    \\\\
    Implementation Personel is responsible for the specific implementation of the codebase as well as testing and ensuring working, performance and
    competitive production results. Implementation Personel is expected to provide acceptable results in reasonable amount of time.
    
    \section{Development Communication Plans}
    The Development Team communication plans will be conducted primarily online, with the exception of conflict resolutions and contract changes to be decided in person.
    Members of developement team should be responsible for their updates on the team's status and quota. An interval of two days is recommended in order to not miss crucial
    informations and executive decisions.
    \\\\
    Team members are expected to be noticed of communication updates and provides reply if necessary in manners of at-most three to five hours since the message departure.

        \subsection{Communication Stack}
        Based on the scope of the project, the communication stack should not be too complicated and based around third party Services, outlined as follow:
        \begin{itemize}
            \item Primary Communication Channel: Discord
            \item Secondary Communication Channel: Email
            \item Project and Task Management Service: Jira
        \end{itemize}

        \subsection{Executive Decision and Conflict Resolution Protocols}
        The Development Team will conduct weekly retrospective survey and forward-looking between 19th hour and 22nd hour at weekend 
        in order to evaluate team's production result as well as
        planning the upcoming development direction; finalizing production materials for submission at each 2-week sprints.
        \\\\
        In order to promote innovative ideas and quick iterative development, Scrum model should be used as the engineering process. The team should be able
        to quickly go through with one's work without fear of failure. After a trial and error process, the finalized ideas that inlined with the project core concept
        are considered to be accepted into main development branch. 
        \\\\
        The process of deciding the integration of changes should be held at all weekends, during the retrospective and forward-looking process, in order to reflects
        changes induced by technical blocks or by other constraints introduced in the development sprint. The process is based on the constrast majority vote system, 
        enabling a quick and and thorough exhanges of ideas through continuous feedback and demonstration. After the demonstration section, final executive decisions are
        relied on Executice Officer for acceptence.
        \\\\
        Conflicts are also part of the process, and undecisive actions of these aspects will cause long-term harm to the project development. Conflicts are to be reported
        directly to Project Manager as per this contract, and violations of contracts terms are also subjected to incident loggings. The Conflicts Resolution Process determines
        if it is necessary to escalate the actions needed.
        \\
        If the Conflicts are affecting less than three of the team's development member, disputes will be handled internally
        by direct communication and case-specific actions. 
        \\
        Otherwise, if the Conflicts affect the majority of the team's developement member, an in person meeting will be held
        to account for the related incidents and consideration to contract changes if it is a major blocking in the team's performance.

        \subsection{Work Schedules and Deadlines}
        The Development Team primarily operates online with flexible schedule, allowing other members to cover each's works while not compromising product quality
        and timing contraints.
        \\\\
        The Development Process is conducted every week, spanning from Monday to Sunday. The ending of each week should be a milestone for product reanalysis and 
        performance assertion. Tasks of each Process iteration will be declared and is expected to be completed in a timely manners based on the given periods.
        \\\\
        The Central Development Process Work Session will be conducted from the 20th hour to 22nd hour on Sunday, where the team will review production assets in order
        to apply Quality Controls and maintaining consistency between different codebases.
        \\\\
        In the case of missing deadlines, the entire development team is responsible to commit mandatory overtime of combined work in order to resolve missing deadlines.
        The responsible team member of the original task will be noticed of the incidents; an unreasonable amount of missing deadlines incidents will be reported to Project
        Manager for further accessment.

        \subsection{Code and Documentation Standards}
        Each individual development team member is responsible for following the Code of Conducting while practicing implementation. The specific coding convention
        is yet to be decided, but a good propotion will be based on C++ Core Guidelines.
        \\
        Individual development team member should prioritize readability and maintainability while implementing functionalities, obfuscation of codebase is yet to be
        necessary and is considered a bad practice in this project.
        \\\\
        Based on the scope of the project, the development operations stack should not be too complicated and based around third party Services, outlined as follow:
        \begin{itemize}
            \item Development Operations and Source Control Service: Github
            \item Project Documents and Assets Storage: Google Drive
        \end{itemize}

        Code testings software is yet to be determined. However, development team member should be responsible for quality working production results and self-penetration
        testing before deliveries.
        \\\\
        Before the finalized decision on core implementation technologies, documentation standards is expected to follow IEEE Standard for Software User Documentation.
        Based on chosen technology, a more flexible and open, autonomous solutions can be used to automate the technical documentation process. Outside of implementation,
        the documentation is to follow the aforementioned standard.

        \subsection{Accountability and Performance}
        Development team members are expected to be on time with assigned tasks, while also maintaining quality in production results. In rare cases when a task period
        is misaligned, further set-back can be applied to accomodate the necessary tasks.
        \\
        Development team members performance will be measured based on their communication participation, their accessment on project responsiblities and their ability to
        provide exceptional results. 
        \\
        Though not necessary, development team member is also encouraged to propose changes to the development pipeline if see fits; but the 
        final decision still relies on both Executive Officer and Project Manager.
        \\\\
        Lack of development participation will results in competency reassement. The Development Team will try to establish common grounds and provides necessary sup­ports
        for each individuals during the handling of underperforming members.
        \\
        However, punishment of course partition degradation will be considered in some cases.
        If incidents are repeated in an unreasonable amount, or conflicts causing blockage in the development process, notification to course instructor 
        will be considered if applicable.
        \\\\
        Lack of team contract adhering will also inherently be processed based on the previously mentioned procedures. Though the Project Manager may consider
        alternative methods such as contract validation in order to determine if the incident is the result of the incomplete nature of this contract or by the
        subjective reasoning of individual.

%\begin{appendices}
%\input{base/acronyms}
%\chapter{Analysis Models}
%\chapter{To Be Determined List}


%\end{appendices}


